### 2018-12-07 Revision/Response/response.tex

\noindent  A more complex problem as suggested by the reviewer would manifest itself into an increased number of
uncertain parameters and/or an increased amount of non-linearity in the system response. Therefore, while
we did not implement the framework to a new system, we have significantly increased the non-linearity of the
response by increasing the degree of uncertainty in the rate parameters. In addition to the rate parameters,
we perturb the initial conditions to investigate their impact on the response individually as well as due to
their interaction with the rate parameters. Hence, we have also increased the dimensionality of the problem.
As expected by the reviewer, the resulting spectral gap between the first two eigenvalues is observed to
decrease for this relative more complex scenario as shown in Figure~1 in the revised manuscript. 
The proposed framework has been used effectively to compute the active subspace, construct a low-dimensional
surrogate, and perform a global sensitivity analysis in this case.

\item \referee{The authors report ignition delay times of 0.1 s (?). See for example Fig. 7 and Tab. 2.
Are these seconds (s)? If this is the case, what kind of conditions (temperature/pressure/stoichiometry)
are the authors considering? They seem very unphysical if the yield an ignition delay time of O(0.1 s).
I could not find any clarification of the initial conditions for the ignition calculations.
This is again a symptom of the disconnect between the authors' aims (a novel method, potentially very useful to the combustion community) and the combustion community's aims (more understanding and tools that can be of help in combustion kinetics).}

\noindent  Depending upon the initial conditions, the ignition delay can range from $\mathcal{O}(10^{-3})$
to $\mathcal{O}(10^3)$ seconds for hydrogen-air mixtures as shown by Starostin et al. in~\cite{Starostin:2011}.
In this work, the initial pressure ($P_0$), temperature ($T_0$), and
the equivalence ratio~($\Phi_0$) considered in the computations are 1~atm, 900~K, and 2.0
respectively. These values have been reported in the revised manuscript in the beginning of
Section 5 on page 15.
In this revision, we perturb the initial conditions to study their impact
on ignition delay estimates. The mean estimate of the ignition delay using data at 10$^4$ random samples in
the 36-dimensional space is found to be approximately 0.15 as reported in Table 2 on page 18 in the
revised manuscript. As mentioned in the paper, we have used 
the TChem software for model predictions and based on our recent communication with the developers at
Sandia National Laboratories, these estimates seem reasonable.

@@

\item \referee{14.8: here and in a few other places, I have an issue with statements like
active subspace is 1-dimensional'. To me, active subspace is as many dimensional as one likes,
so the statement should be changed to something like '1-dimensional active subspace captures
most of the variance/uncertainty/dynamics etc..', or '1-dimensional active subspace provides
very accurate approximation...'.}

\noindent The reviewer's suggestion has been incorporated in the revised manuscript.

\item \referee{14.57: even if nominal is zero, one could perturb them, right? 
Or it is actually indicating the fact that there should be no exponential factor whatsoever.}

\noindent Based on our conversations with the developers of the TChem software at Sandia
National Laboratories, we decided not to perturb the activation energies with a 0
nominal value since the exponential factor is not considered for these reactions, as mentioned
by the reviewer.

### 2018-12-08 Revision/Paper/app.tex
..
...

For the high-dimensional case, we aim to investigate the impact of the uncertain
pre-exponents ($A_i$'s) as well as the activation energies ($E_{a,i}$'s) \rebut{and
the initial conditions: pressure~($P_0$), temperature~($T_0$), and stoichiometry based on
the equivalence ratio~($\Phi_0$)} on ignition delay during the H$_2$/O$_2$ reaction. 
\rebut{The $\log(A_i)$'s, $E_{a,i}$'s for all reactions except 
$\mathcal{R}_6$ -- $\mathcal{R}_9$, $\mathcal{R}_{13}$ (due to 
zero nominal values for $E_a$), and the initial conditions were perturbed by
2$\%$ about their nominal values. Note that the mangnitude of the perturbation
was selected such that the ignition delay remains positive throughout the input
domain. The nominal values of the rate parameters, $A_i$'s and $E_{a,i}$'s 
were taken from~\cite{Yetter:1991}. The nominal values of $P_0$, $T_0$, and
$\Phi_0$ were considered to be 1.0 atm, 900~K, and 2.0 respectively.}

>>>>

For the high-dimensional case, we aim to investigate the impact of 
uncertainty in the following problem parameters on 
the ignition delay associated with the H$_2$/O$_2$ reaction:
(i) pre-exponents ($A_i$'s); (ii) the activation energies
($E_{a,i}$'s); and (iii) \rebut{the initial pressure~($P_0$),
temperature~($T_0$), and stoichiometry~($\Phi_0$)}. 
%
\rebut{The $\log(A_i)$'s, $E_{a,i}$'s for all reactions except $\mathcal{R}_6$
-- $\mathcal{R}_9$, $\mathcal{R}_{13}$ (due to zero nominal values for $E_a$),
and the initial conditions were perturbed by 2$\%$ about their nominal values.
Note that the mangnitude of the perturbation was selected such that the
ignition delay assumes a physically meaningful value in the input domain. 
The nominal values of the rate parameters, $A_i$'s and $E_{a,i}$'s 
were taken from~\cite{Yetter:1991}. The nominal values of $P_0$, $T_0$, and
$\Phi_0$ were considered to be 1.0 atm, 900~K, and 2.0 respectively.}

### 2018-12-08 Revision/Paper/intro.tex
...

An alternate strategy to dimension reduction involves computing the global
sensitivity measures associated with the uncertain inputs of a model. Depending
upon the estimates of the sensitivity measures, only the important inputs are
varied for the purpose of uncertainty quantification (UQ). Sobol' indices are
commonly used as global sensitivity measures~\cite{Sobol:2001}. They are
used to quantify the relative contributions of the uncertain inputs to the variance
in the output, either individually, or in combination with other inputs. 
Multiple efforts have focused on efficient computation of the Sobol' 
indices~\cite{Sudret:2008,Plischke:2013,Tissot:2015,Li:2016} including the 
derivative-based global sensitivity measures~(DGSMs), developed to
compute approximate upper bounds for the Sobol' indices with much fewer
computations~\cite{Sobol:2009, Lamboni:2013}. It was noted
in~\cite{Diaz:2016,Constantine:2017} that DGSMs can be approximated by
exploiting their links with active subspaces. This led to the definition of the 
so-called \emph{activity scores}. In Section~\ref{sub:gsa}, we build on these
ideas to provide a complete analysis of links between Sobol indices, DGSMs, and
activity scores for functions of independent random inputs whose distribution
law belongs to the class of Boltzmann probability measures. 
It is worth mentioning that computing global sensitivity measures provides 
important information about a model that go beyond dimension reduction. By 
identifying parameters with significant impact on the model output, we can assess
regimes of validity of the model formulation, and gain critical insight into the
underlying physics in many cases.

>>>>

An alternate strategy to dimension reduction involves computing the global
sensitivity measures associated with the uncertain inputs of a model. Depending
upon the estimates of the sensitivity measures, only the important inputs are
varied for the purpose of uncertainty quantification (UQ). Sobol' indices are
commonly used as global sensitivity measures~\cite{Sobol:2001}. They are
used to quantify the relative contributions of the uncertain inputs to the variance
in the output, either individually, or in combination with other inputs. 
Multiple efforts have focused on efficient computation of the Sobol' 
indices~\cite{Sudret:2008,Plischke:2013,Tissot:2015,Li:2016} including the 
derivative-based global sensitivity measures~(DGSMs), developed to
compute approximate upper bounds for the Sobol' indices with much fewer
computations~\cite{Sobol:2009, Lamboni:2013}. It was noted
in~\cite{Diaz:2016,Constantine:2017} that DGSMs can be approximated by
exploiting their links with active subspaces. This led to the definition of the 
so-called \emph{activity scores}. In Section~\ref{sub:gsa}, we build on these
ideas to provide a complete analysis of links between Sobol indices, DGSMs, and
activity scores for functions of independent random inputs whose distribution
law belongs to a \rebut{broad class of probability measures.} 
It is worth mentioning that computing global sensitivity measures provides 
important information about a model that go beyond dimension reduction. By 
identifying parameters with significant impact on the model output, we can assess
regimes of validity of the model formulation, and gain critical insight into the
underlying physics in many cases.
